Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-07 minimax.tex
pgfplots version
removing the paragraph about structure of the paper in the introduction

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}

@@

The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective and
\Cref{sec:background} provides the necessary background. In \cref{sec:mmr} we provide a method for robust winner determination using the minimax criterion. %, a method that selects a winner that minimizes the worst possible regret.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.

@@

\begin{figure}
	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	\begin{tikzpicture}
		\pgfplotsset{
			every axis legend/.append style={
				at={(0.5,1.03)},
				anchor=south
			},
		}
		\begin{semilogyaxis}[
			legend columns=3,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			log basis y= 10,
			ymin=10e-2,
			ymax=10e2,
			ytick={10e-2,1,2,10,15,20,30,146},
			yticklabels={0.01,1,2,10,15,20,30,146},
			ymajorgrids=true,
			ytick style={draw=none},
			xmin=0,
			xmax=1000,
			xtick={0,100,200,300,400,500,600,700,800,900,1000},
			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
			ticklabel style = {font=\tiny}
			]

>>>>

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}

@@

%NOTE: the structure of the article is perhaps self evident...
%The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective and
%\Cref{sec:background} provides the necessary background. In \cref{sec:mmr} we provide a method for robust winner determination using the minimax criterion. %, a method that selects a winner that minimizes the worst possible regret.
%In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.

@@

\begin{figure}
	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	\begin{tikzpicture}
		\pgfplotsset{
			every axis legend/.append style={
				at={(0.5,1.03)},
				anchor=south,
			},
		}
		\begin{semilogyaxis}[
			legend columns=3,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			log basis y= 10,
			ymin=10e-2,
			ymax=10e2,
			ytick={10e-2,1,2,10,15,20,30,146},
			yticklabels={0.01,1,2,10,15,20,30,146},
			ymajorgrids=true,
			ytick style={draw=none},
			xmin=0,
			xmax=1000,
			xtick={0,100,200,300,400,500,600,700,800,900,1000},
			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
			ticklabel style = {font=\tiny}
			]
